PineAPPL: EW and mixed QCD--EW corrections for PDF fits

### 2020-07-28 paper/paper.tex
typo
Change the title to something more meaningful

\title{Including EW and mixed QCD-EW corrections into PDF fits}

@@

\acknowledgments
We are grateful to Rikkert Frederix for discussions and explanation about
\textsc{aMCfast}. We acknowledge discussions with 
Florencia Canelli, Stefano Camarda, Paolo Francavilla, Abideh Jafari, Andreas Jung, Elizaveta Shabalina, Wolfgang Wagner about the 
treatment of EW effects in experimental data. \\
%Alessandro Vicini\\
E.R.N. is supported by the European Commission through the Marie
Sk\l odowska-Curie Action ParDHonS FFs.TMDs (grant number 752748).
C.S.\ is supported by the European Research Council under the European Union's
Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).
MZ thanks the Nikhef institute in Amsterdam,
where he was employed during the early stages of this paper.

>>>>

\title{PineAPPL: EW and mixed QCD--EW corrections for PDF fits}

@@

\acknowledgments
We are grateful to Rikkert Frederix for discussions and explanations about
\textsc{aMCfast}. We acknowledge discussions with 
Florencia Canelli, Stefano Camarda, Paolo Francavilla, Abideh Jafari, Andreas Jung, Elizaveta Shabalina, Wolfgang Wagner about the 
treatment of EW effects in experimental data. \\
%Alessandro Vicini\\
E.R.N. is supported by the European Commission through the Marie
Sk\l odowska-Curie Action ParDHonS FFs.TMDs (grant number 752748).
C.S.\ is supported by the European Research Council under the European Union's
Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).
MZ thanks the Nikhef institute in Amsterdam,
where he was employed during the early stages of this paper.
